Light inextensible strings under tension in the Schwarzschild geometry

### 2019-02-27 string_ajp.tex
discuss null geodesics

Taking strings for which $r>1$ first,
figure~\ref{closest_approach_non_self_intersecting} shows a sequence
of non-self-intersecting numerical solutions to
equation~\ref{rdashdash}, rotated so that the tangential point of
closest approach occurs at~$\phi=0$.
Figure~\ref{closest_approach_self_intersecting} shows the
corresponding diagram for self-interesecting strings.  A bisection
technique reveals that if the closest approach is greater than a
critical value of~$\simeq 1.076109317(1)$, the string does not
self-intersect; if the closest approach is less than this value, then
the string crosses itself at~$\phi=\pi/2$.  As discussed above, if
$\left(r'\right)^2=2r(r-1)$, the string has a point of inflection at
which point the radius of curvature becomes infinite.
Figure~\ref{curvature_switch} shows non-self intersecting strings
rotated so that the point of inflection occurs at~$\phi=0$; we see
that the strings have a finite length in which convex to the origin
and two semi-infinite stretches in which the curvature goes the other
way.

@@

>>>>

Taking strings for which $r>1$ first,
figure~\ref{closest_approach_non_self_intersecting} shows a sequence
of non-self-intersecting numerical solutions to
equation~\ref{rdashdash}, rotated so that the tangential point of
closest approach occurs at~$\phi=0$.
Figure~\ref{closest_approach_self_intersecting} shows the
corresponding diagram for self-interesecting strings
(figure~\ref{light_closest_approach} shows comparable null geodesic
diagram for comparison).  A bisection technique reveals that if the
closest approach is greater than a critical value of~$\simeq
1.076109317(1)$, the string does not self-intersect; if the closest
approach is less than this value, then the string crosses itself
at~$\phi=\pi/2$.  As discussed above, if $\left(r'\right)^2=2r(r-1)$,
the string has a point of inflection at which point the radius of
curvature becomes infinite.  Figure~\ref{curvature_switch} shows
non-self intersecting strings rotated so that the point of inflection
occurs at~$\phi=0$; we see that the strings have a finite length in
which convex to the origin and two semi-infinite stretches in which
the curvature goes the other way.

@@

\begin{figure}[p] % Created by "light_closest_approach.R"
\centering
\includegraphics[width=170mm]{light_closest_approach.pdf}
\caption{Null geodesics in the Schwarzschild geometry starting~$(r,0)$
  and initially tangential.  Note the differences between these curves
  and the taut strings shown elsewhere: unlike taug strings, null
  geodesics have positive curvature everywhere, may cross the event
  horizon inwards, and are never tangential to the event horizon}
\label{light_closest_approach}
\end{figure}
